Reproducibility in plant pathology: where do we stand and a way forward

### 2022-04-30 analysis/paper/paper.Rmd
Response to reviewer 2, L164 comment
Respond to reviewer 2 L154 comment

It goes without saying that plant pathologists already provide information on protocols and chemicals allowing for reproducibility.
However, biological specimens such as strains, cultures or cultivars are not available.
These cases do constitute a lack of reproducibility but will not be covered here.

@@

Only `r as.character(english(length(which(rrpp$reproducibility_score == 100))))` articles scored '100' or fully reproducible (Figure \@ref(fig:reproScore)).

>>>>

It goes without saying that plant pathologists already provide information on protocols and chemicals allowing for reproducibility.
However, frequently biological specimens such as strains, cultures or cultivars are often not available.
These cases do constitute a lack of reproducibility but will not be covered here.

@@

Only `r as.character(english(length(which(rrpp$reproducibility_score == 100))))` articles scored '100%' or fully reproducible (Figure \@ref(fig:reproScore)).
